The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-04-26 paper.qmd
started doing the r code for the maps

![This shows the user interface for the experiment performed by @Hofmann2012. The question of "furthest to the right" is open to interpretation.  ](furthestright.png){#fig-right width=50%}

@@

```{r}

```

>>>>

![This shows the user interface for the experiment performed by @Hofmann2012. The question of "furthest to the right" is open to interpretation.](furthestright.png){#fig-right width=50%}

@@

```{r}
#| eval: false
#| echo: false

# seed for sampling
set.seed(1997)

# load libraries
library(strayr)
library(tidyverse)
library(biscale)

# Get map data
sa4 <- read_absmap("sa42021")
state <- read_absmap("state2021")

# Add Spatial trend
state <- state |>
  dplyr::mutate(temp = 30 - 0.001*(cent_long-110)^(2) - 0.003*(cent_lat-12.52294)^(2), # trend
         notrend = rnorm(1), # no trend
         highvar = runif(10, min=4, max=5), # high variance
         lowvar = runif(10, min=0, max=1), # low variance
         )

sa4 <- sa4 |>
  dplyr::mutate(temp = 30 - 0.001*(cent_long-123.7799)^(2) - 0.003*(cent_lat-12.52294)^(2), # trend
         notrend = rnorm(1), # no trend
         highvar = runif(1, min=4, max=5), # high variance
         lowvar = runif(1, min=0, max=1), # low variance
         )

# Choropleth Map
state %>%
  ggplot() +
  geom_sf(aes(fill = temp, geometry = geometry)) + 
  scale_fill_distiller(type = "seq", palette = "YlOrRd", direction = 1)

# Bivariate Map
# Method 1
d<-expand.grid(x=1:100,y=1:100)
ggplot(d, aes(x,y,fill=atan(y/x),alpha=x+y))+
  geom_tile()+
  scale_fill_distiller(type = "seq", palette = "YlOrRd", direction = 1) +
  theme(legend.position="none",
        panel.background=element_blank())+
  labs(title="A bivariate color scheme (Viridis)")

state <- state %>%
  dplyr::mutate(x=100*(temp-min(temp))/max(temp),
         y=100*highvar/max(highvar))

ggplot() +
  geom_map(data =cmap, map = cmap,
           aes(x = long, y = lat, map_id = id),
           color = "#2b2b2b", size = 0.05, fill = NA) +
  geom_map(data = filter(counties@data,year==2015), map = cmap,
           aes(fill =atan(y/x),alpha=x+y, map_id = fips),
           color = "gray50") +
  #add black state borders (just to see if things are working)
  geom_map(data = smap, map = smap,
           aes(x = long, y = lat, map_id = id),
           color = "black", size = .5, fill = NA) +
  theme_map(base_size = 12) +
  theme(plot.title=element_text(size = 16, face="bold",margin=margin(b=10))) +
  theme(plot.subtitle=element_text(size = 14, margin=margin(b=-20))) +
  theme(plot.caption=element_text(size = 9, margin=margin(t=-15),hjust=0)) +
 # scale_fill_gradient(low="red",high="blue")
  scale_fill_viridis()+guides(alpha=F,fill=F)+
  labs(caption="@lenkiefer Source: U.S. Census Bureau",
       title="Housing units and Population growth 2010-2015",
       subtitle="Bivariate choropleth")

# Method 2

custom_pal <- c(
  "1-1" = "#d3d3d3", # low x, low y
  "2-1" = "#9e3547", 
  "3-1" = , 
  "4-1" = , # high x, low y
  "1-2" = "#4279b0", # low x, high y
  "2-2" = "#311e3b" # high x, high y
)

library(RColorBrewer)
rev(brewer.pal(9, name = "YlOrRd"))
names <- paste(rep(1:9, 9), "-" , rep(1:9, each=9), sep="")

# Pixel Map
# Sample Map
```
